---
title: "Create Codelist"
subtitle: "Narcolepsy"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Load pkgs and funs

```{r, class.source = 'fold-show'}
# R packages
library(reactable)
library(tidyverse)
library(here)
library(dbplyr)
library(readr)
library(bigrquery)
library(DBI)

# Helper fun connecting to bigquery
source(here("scripts/connect_bigquery.R"))

# Helper function to write SQL queries
source(here("scripts/create_ingredient_lookup_sql.R"))

```

# Define ingredients

```{r, class.source = 'fold-show'}
# Define product list for lookup
ingredient_list <- c('Sodium Oxybate', 
                     'Pitolisant', 
                     'Solriamfetol', 
                     'Modafinil', 
                     'Dexamfetamine',
                     "Methylphenidate")
```

# Create SQL query

- including wildcards at the beginning and end
- Case insensitive search using LOWER function
- This code also gets `ddd` information from the `dmd.ddd` table

```{r, class.source = 'fold-show'}

# With wildcards
sql_wild_ingredients <- create_ingredient_lookup_sql(ingredient_list, 
                                                     wildcards = TRUE,
                                                     return = "sql")
```

## Show SQL query

```{r, class.source = 'fold-show'}
cat(sql_wild_ingredients)
```

# Show results

```{r}
df_ingredients <- dplyr::tbl(conn_ebm_dmd, sql_wild_ingredients) %>% 
  collect()

df_ingredients %>% 
  reactable(filterable = TRUE,
            columns = list(
              type = reactable::colDef(minWidth = 40),
              id = reactable::colDef(minWidth = 100),
              bnf_code = reactable::colDef(minWidth = 100),
              nm = reactable::colDef(minWidth = 200),
              ingredient = reactable::colDef(minWidth = 100),
              ddd = reactable::colDef(minWidth = 30)
            ),
            style = list(fontSize = "12px"),
            highlight = TRUE,
            defaultPageSize = nrow(df_ingredients))
```

## ddd availability

The table below shows the number of products (`n`) with available daily defined dose (`ddd_available`) information in our database.
More information can be found in the table with detailed information at the end of this document.

```{r}

df_ingredients %>% 
  group_by(ingredient) %>% 
  count("ddd_available" = !is.na(ddd), name = "n") %>% 
  reactable(filterable = TRUE,
            style = list(fontSize = "12px"),
            highlight = TRUE)
```


# Export codelist to .csv

- The .csv file is available [here](https://github.com/ebmdatalab/scmd-narcolepsy/blob/update-codelist/data/narcolepsy-meds.csv)

```{r}
# Write csv codelist 
write_csv(df_ingredients, file = here("data/narcolepsy-meds.csv"))
```

